---
title: "Penguins ANOIVA"
author: "Joslyn Fritz"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load Packages and read - in penguins.csv

```{r}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")

```

Our question is, is there a sig diff among penguins of their flipper length by species. (Chinstrap, Gentoo, Adelie?)


2. Do some exploring in tidy format

New functions: with + table for easy counting over multiple factors 

Updated species name using case_when


```{r}

counts <- with(penguins, table(species, sex))
counts

penguins2 <- penguins %>% 
  mutate(common_name = case_when(
    species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap", 
    species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo", 
    species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
  )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

penguins2
```

- Exploratory graphs
- Summary statistics
- Levene's test for equal variances 
- one-way anova
- post-hoc testing

central limit theorem means our means will be normally distributed

```{r}

hists <- ggplot(penguins2, aes(x = flipper_length)) +
  geom_histogram(aes(fill = common_name)) + 
  facet_wrap(~common_name)

hists

qq_penguin <- ggplot(penguins2, aes(sample = flipper_length)) +
  geom_qq(aes(color = common_name)) + 
  facet_wrap(~common_name)
qq_penguin


# Levene's test for equal variances (> 2 groups.. if you have two groups use the f-test for equal variances)

# we'll use the function leveneTest from the 'car' package

# Null = variances are equal
# HA = variances are not equal

penguin_levene <- leveneTest(flipper_length ~ common_name, data = penguins2)
penguin_levene

# we reain the null hypothesis of equal variances (p = 0.06)

penguin_var <- penguins2 %>% 
  group_by(common_name) %>% 
  summarize(
    variance = var(flipper_length)
  )
penguin_var
```

We're asking if the samples are different enough to be from the same population.

if the largest variance is less than 4x the smallest, still do the extra testing. 







