---
title: "Penguins ANOIVA"
author: "Joslyn Fritz"
date: "11/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load Packages and read - in penguins.csv

```{r}
library(tidyverse)
library(car)
library(onewaytests)

penguins <- read_csv("penguins.csv")

```

Our question is, is there a sig diff among penguins of their flipper length by species. (Chinstrap, Gentoo, Adelie?)


2. Do some exploring in tidy format

New functions: with + table for easy counting over multiple factors 

Updated species name using case_when


```{r}

counts <- with(penguins, table(species, sex))
counts

penguins2 <- penguins %>% 
  mutate(common_name = case_when(
    species == "Chinstrap penguin (Pygoscelis antarctica)" ~ "Chinstrap", 
    species == "Gentoo penguin (Pygoscelis papua)" ~ "Gentoo", 
    species == "Adelie Penguin (Pygoscelis adeliae)" ~ "Adelie"
  )) %>% 
  select(-species) %>% 
  filter(sex == "FEMALE")

penguins2
```

- Exploratory graphs
- Summary statistics
- Levene's test for equal variances 
- one-way anova
- post-hoc testing





